Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-09 content/impl.tex

\otodo{The following definitions are very general, and not related to the transformation.
    Can we move them somewhere earlier?}
\paragraph{Edge Functions}\label{sec:ef}

@@

  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.

\otodo{incorporate into previous section}
\subsection{Defining IFDS and IDE Problems}
In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.

\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
Recall that an IFDS problem instance is defined as a five-tuple
\[
    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
\]
where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.

@@

The meaning of an edge in the exploded supergraph is the following.
Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$. Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds. Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
\otodo{Here, you defined the output of a transformation as just G\# and an edge function. Later, you also include the lattice. Should we include the lattice here?}
Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,(\top,\,\bot),\,\edgefn)$
converts it into an equivalent IDE problem with a two-point lattice. We consider two transformations:
\begin{itemize}
	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
\end{itemize}
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

>>>>

  \commentout{
\otodo{The following definitions are very general, and not related to the transformation.
    Can we move them somewhere earlier?}
\paragraph{Edge Functions}\label{sec:ef}

@@

  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
  }

\otodo{incorporate into previous section}
\subsection{Defining IFDS and IDE Problems}
%In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.

\commentout{
\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
Recall that an IFDS problem instance is defined as a five-tuple
\[
    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
\]
where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.

@@

The meaning of an edge in the exploded supergraph is the following.
Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$. Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds. Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
}

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
converts it into an equivalent IDE problem. We consider two transformations:
\begin{itemize}
	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
\end{itemize}
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
